R Notebook

### 2022-06-02 Code/Simulation.Rmd
added code for alternative method using arma(1,1) structure

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

```{r ARMA(1, 1) D}
ptm <- proc.time()

@@

>>>>

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
library(tseries)
source('tspb.R')
```

@@

```{r ARMA(1,1) D}
ptm <- proc.time()

@@

```{r AR(1) D2}
test_copula_D2 <- function(x, pdist, qdist, ..., B) {

    ## Get observed statistic
    n <- length(x) 
    stat  <- ks.test(x, pdist, ...)$statistic

    ## transform the data to standard normal scale and fit arma(1,1)
    zx <- qnorm(rank(x) / (n + 1))
    fit <- tseries::arma(zx, include.intercept = FALSE)

    ar <- fit$coef[1]
    ma <- fit$coef[2]

    ## Perform parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        ## 1. The marginal distribution is the fitted dist
        ## 2. There is arma(1,1) dependence on the normal scale
        zx.b <- arima.sim(list(ar = ar, ma = ma), 
                          rand.gen=rnorm, 
                          sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                          n = n) # simulate from fit
        u <- pnorm(zx.b)
        # Transform bootstrap sample and fit the parameters
        x.b <- qdist(u, ...)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, pdist, ...)$statistic
    }

test_standard_ks <- function(x, pdist, ...) {
  p.value <- ks.test(x, pdist, ...)$p.value
  list(p.value = p.value)
}

# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar), rand.gen=rnorm, sd = sqrt(1 - ar^2), n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

save(results, file = "results_ar1_D2.RData")

# Generate histograms plot
hist_ar1_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar1_D2
```

```{r MA(1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ma = ma), rand.gen = rnorm, sd = sqrt(1/(1+ma^2)), n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

save(results, file = "results_ma1_D2.RData")

# Generate histograms plot
hist_ma1_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ma1_D2
```

```{r ARMA(1,1) D2}
# Set variables
n <- 100
ar <- 0.5
ma <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(ar = ar, 
                                                           ma = ma), 
                                                      rand.gen=rnorm, 
                                                      sd = sqrt((1-(ar^2))/(1+2*ar*ma+ma^2)), 
                                                      n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

save(results, file = "results_arma_D2.RData")

# Generate histograms plot
hist_arma_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_arma_D2
```

```{r AR(2) D2}
# Set variables
n <- 100
b1 <- 0.5
b2 <- 0.3
counter <- 0
nrep <- 1000
B <- 1000
mean <- 0
sd <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                              pnorm, 
                                              qnorm,
                                              mean = mean, 
                                              sd = sd,
                                              B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(arima.sim(list(order = c(2, 0, 0), 
                                                           ar = c(b1, b2)),
                                                      rand.gen=rnorm,
                                                      sd = sqrt(((1+b2)*(1-b2-b1)*(1-b2+b1))/(1-b2)),
                                                      n = n), 
                                                pnorm,
                                                mean = mean, 
                                                sd = sd)$p.value)

save(results, file = "results_ar2_D2.RData")

# Generate histograms plot
hist_ar2_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_ar2_D2
```

```{r hist_ar1_ma1_arma_ar2_D2}
load('results_ar1_D2.RData')
model <- rep("AR(1)", 2000)
ar1 <- data_frame(results, model)

load('results_ma1_D2.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, model)

load('results_arma_D2.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, model)

load('results_ar2_D2.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, model)

data <- rbind(ar1, ma1, arma, ar2)

data$model <- factor(data$model, levels = c("AR(1)", "MA(1)", "ARMA(1, 1)", "AR(2)"))
data$histogram <- factor(data$histogram, levels = c("Naive", "Copula"))

# Generate histograms plot
hist_ar1_ma1_arma_ar2_D2 <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y", ncol = 4)
hist_ar1_ma1_arma_ar2_D2

ggsave(filename = "hist_ar1_ma1_arma_ar2_D2.pdf", plot = hist_ar1_ma1_arma_ar2_D2, path = "../Manuscript", height = 4.2, width = 6)
```

```{r Gamma D2}
# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
shape <- 3
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                             pgamma, 
                                             qgamma,
                                             shape = shape,
                                             scale = scale,
                                             B = B))
counter <- 0

# P-vals from naively using fitted parameters
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgamma, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                pgamma,
                                                shape = shape,
                                                scale = scale)$p.value)

save(results, file = "results_gamma_D2.RData")

# Generate histograms plot
hist_gamma_D2 <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gamma_D2
```

```{r GEV D2}
# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 1000
loc <- 0
shape <- 0.2
scale <- 1

# P-vals from using bootstrap with copulas
pvals_copula <- replicate(nrep, test_copula_D2(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho),
                                               pgev,
                                               qgev,
                                               loc = loc, 
                                               shape = shape,
                                               scale = scale,
                                               B = B))
counter <- 0

# P-vals from standard KS test
pvals_naive <- replicate(nrep, test_standard_ks(genData(n, qgev, loc = loc, shape = shape, scale = scale, copula = normalCopula, rho = rho), 
                                                 pgev,
                                                 loc = loc, 
                                                 shape = shape,
                                                 scale = scale)$p.value)

save(results, file = "results_gev_D2.RData")

# Generate histograms plot
hist_gev_D <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_gev_D
```

```{r hist_gamma_gev_D2}
load('results_gamma_D2.RData')
model <- rep("Gamma", 2000)
gamma <- data_frame(results, model)

load('results_gev_D2.RData')
model <- rep("GEV", 2000)
gev <- data_frame(results, model)

# Generate histograms plot
hist_gamma_gev_D2 <- ggplot(data) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(histogram~model, scales = "free_y")
hist_gamma_gev_D2

ggsave(filename = "hist_gamma_gev_D2.pdf", plot = hist_gamma_gev_D2, path = "../Manuscript", height = 4.2, width = 6)
```
